Approximation as Differentiation

### 2025-04-12 appendix/notes/cmon-enriched.tex
Going into a bit too much detail here..

\noindent The idempotence of $\bullet$ (together with commutativity and associativity) induces a partial order
$\le_\bullet$ on $X$, with $x \le_{\bullet} y \iff x \bullet y = x$. With respect to this partial order, $x
\bullet y$ is the greatest lower bound (meet) of $x$ and $y$ and $\varepsilon$ is the top element; with
respect to the opposite order, $x \bullet y$ is the least upper bound (join) of $x$ and $y$ is the bottom
element. This thus provides the standard algebraic characterisation of the (dual) order-theoretic notions of
bounded meet semilattices $(X, \top, \meet)$ and bounded join semilattices $(X, \bot, \join)$.

>>>>

\noindent The idempotence of $\bullet$ (together with commutativity and associativity) induces a partial order
$\le_\bullet$ on $X$, with $x \le_{\bullet} y \iff x \bullet y = x$. With respect to this partial order, $x
\bullet y$ is the greatest lower bound (meet) of $x$ and $y$ and $\varepsilon$ is the top element; with
respect to the opposite order, $x \bullet y$ is the least upper bound (join) of $x$ and $y$ is the bottom
element. This therefore provides an algebraic characterisation of the (dual) order-theoretic notions of
bounded meet semilattices $(X, \top, \meet)$ and bounded join semilattices $(X, \bot, \join)$.
